ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-08 paper.tex
addressed cuneo's other comments

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji.jpg}
	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
	\label{fig:kinkakuji}
\end{figure}

@@

With no access to \texttt{systemctl} we could not use the custom systemd service
we wrote to manage the server daemon. Instead, we used a custom shell script and
an npm package called ``forever'' to handle starting and stopping it. The
forever package runs Node.js scripts continuously, automatically restarting them
if they crash~\autocite{robbins2019}.

Tours are stored on the server as compressed zip files, but when uploading or
editing a tour these zips are decompressed to a temporary directory. To prevent
the server's limited disk space from filling up with old temporary files we
wrote a simple bash script that removes directories that have not been modified
in the past five days. We set up a cron job\footnote{The program cron allows for
periodic scheduling of repeated commands} to run this script automatically once
per day to clean out old temporary files that are not being used any more.

@@

Additionally, we would not try to use any text recognition or translation APIs
to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
that this kind of technology needs to mature before it is completely usable,
especially for Japanese. Instead, we had Atticus share a Google Sheets
spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
his decision-making process about each translation. Once this time-intensive
labor was completed, we took each field of translated text from the spreadsheet
and implemented it directly into the app, associating each translation with the
correct image target.

@@

At this point in the project, the codebase for Editour was already around three
thousand lines of vanilla JavaScript. With the changing requirements, Editour
was becoming onerous to maintain at this stage of the project. Luckily, these
changes were still manageable to implement.

@@

% TODO remove this
\nocite{harvey2002} % don't remove this

@@

% TODO move the stuff about the algorithm into the implementation section
One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a proof
but should at least make it clear why this works. This algorithm's time
complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
all of the polygons being tested~\autocite{geeksforgeekspolygon}.

@@

Throughout the duration of the project, the goalposts shifted multiple times.
This section details some of the initial plans that we explored before Atticus
shifted our focus to a walking tour app with AR features.

@@

We explained the technical hurdles of this concept to Atticus. Ultimately, our
focus shifted away from this idea for other logistical reasons. Initially,
Atticus introduced the possibility of working closely with artists Kishi Bashi
or Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
Yannick Paget is a French musician that became established in Japan. He is both
conductor and composer, originally trained as a professional pianist and
percussionist. He has written music for theater, film and orchestras around the
world. Many of his original compositions were inspired by his experience living
in Japan, such as Tears of Sakura
(\begin{CJK}{UTF8}{min}サクラの涙\end{CJK})~\autocite{yannickpaget2016}. Kishi
Bashi was born in Seattle and grew up in Virginia. Kishi Bashi has appeared at
many major music festivals, toured the US extensively, and has even released his
own line of coffee. His latest album, Omoiyari, was released on May
31\textsuperscript{st}, 2019~\autocite{kishibashi2019}.

@@

Atticus Sims proposed the idea of working with Michael Whittle, a British artist
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo and group exhibitions across the world,
including Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}.
Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, ``Portraits of Thought.'' This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}

>>>>

@@

With no access to \texttt{systemctl} we could not use the custom systemd service
we wrote to manage the server daemon. Instead, we used a custom shell script and
an npm package called \texttt{forever} to handle starting and stopping it. The
forever package runs Node.js scripts continuously, automatically restarting them
if they crash~\autocite{robbins2019}.

Tours are stored on the server as compressed zip files, but when uploading or
editing a tour these zips are decompressed to a temporary directory. To prevent
the server's limited disk space from filling up with old temporary files we
wrote a simple bash script that removes directories that have not been modified
in the past five days. We set up a \texttt{cron} job\footnote{The program
\texttt{cron} allows for periodic scheduling of repeated commands} to run this
script automatically once per day to clean out old temporary files that are not
being used any more.

@@

Additionally, we would not try to use any text recognition or translation APIs
to automate the translation. Figure~\ref{fig:translateInstant} demonstrates that
this kind of technology needs to mature before it is completely usable,
especially for Japanese. Instead, we had Atticus share a Google Sheets
spreadsheet. A Japanese student and acquaintance of Atticus Sims, Hikaru Inoue,
manually translated each sign and provided notes about his decision-making
process about each translation. Once this time-intensive labor was completed, we
took each field of translated text from the spreadsheet and implemented it
directly into the app, associating each translation with the correct image
target.

@@

At this point in the project, the codebase for Editour was already around three
thousand lines of vanilla JavaScript. The growing code complexity meant that
adding features required nontrivial amounts of retesting and refactoring.
Luckily, these changes were still manageable to implement.

@@

@@

% TODO move the stuff about the algorithm into the implementation section
One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an odd number of line
segments.  The point is outside of the polygon if the ray intersects an even
number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a proof
but should at least make it clear why this works. This algorithm's time
complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
all of the polygons being tested~\autocite{geeksforgeekspolygon}.

@@

Throughout the duration of the project, the goalposts shifted multiple times.
This section details some of the initial plans that we explored before the
specifications provided to us by Kyoto~VR helped focus the design on a walking
tour app with AR features.

@@

We explained the technical hurdles of this concept to Atticus. Ultimately, our
focus shifted away from this idea for other logistical reasons. Initially,
Atticus introduced the possibility of working closely with artists Kishi Bashi
or Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
Yannick Paget is a French musician that became established in Japan. He is both
conductor and composer, originally trained as a professional pianist and
percussionist. He has written music for theater, film and orchestras around the
world. Many of his original compositions were inspired by his experience living
in Japan, such as Tears of Sakura
(\begin{CJK}{UTF8}{min}サクラの涙\end{CJK})~\autocite{yannickpaget2016}. Kishi
Bashi was born in Seattle and grew up in Virginia. Kishi Bashi has appeared at
many major music festivals, toured the US extensively, and has even released his
own line of coffee. His latest album, Omoiyari, was released on May
31\textsuperscript{st}, 2019~\autocite{kishibashi2019}. While the prospect of
working with either of these artists had us excited, Kyoto~VR was not able to
find an arrangement.

@@

Atticus Sims proposed the idea of working with Michael Whittle, a British artist
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo and group exhibitions across the world,
including Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}.
Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, \textit{Portraits of Thought}. This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of \textit{Portraits of Thought},
    accessible from the web}
	\label{fig:exhibitionScan}
\end{figure}
